Democracy, Public Support, and Measurement Uncertainty

### 2021-07-29 paper/dcpo_demsupport.Rmd
compile pdf @sammo3182

```{r num-pointAJPS, results='asis', eval=TRUE}
tb_result_cls <- map(result_clsAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

```{r num-pureAJPS, results='asis', eval=TRUE}
tb_result_pureAJPS <- map(result_pureAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

```{r num-expAJPS, results='asis', eval=TRUE}
tb_result_expAJPS <- map(result_expAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

```{r num-pureAPSR, results='asis', eval=TRUE}
tb_result_pureAPSR <- map(result_pureAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

@@

```{r moc-estimates, eval=TRUE}

result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
mocresult_correctAJPS <- readRDS(here("output", "estimates_moc_correctAJPS.RDS"))
mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
mocresult_correctAPSR <- readRDS(here("output", "estimates_moc_correctAPSR.RDS"))
mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))

>>>>

```{r num-pointAJPS, results='asis', eval=TRUE}
tb_result_cls <- purrr::map(result_clsAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

```{r num-pureAJPS, results='asis', eval=TRUE}
tb_result_pureAJPS <- purrr::map(result_pureAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

```{r num-expAJPS, results='asis', eval=TRUE}
tb_result_expAJPS <- purrr::map(result_expAJPS, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)})

@@

```{r num-pureAPSR, results='asis', eval=TRUE}
tb_result_pureAPSR <- purrr:::map(result_pureAPSR, ~ {
  names(.) <- c("tidy", "glance")
  class(.) <- "modelsummary_list"
  return(.)}) %>% 
  .[c("pooled1", "pooled-regime1", "fd1", "fd-regime1",
      "pooled2", "pooled-regime2", "fd2", "fd-regime2")]

@@
